Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores. II. Nanoflare Trains

### 2016-08-28 tex/paper.tex
fixing tikz include to import
final edits for content before submitting to ApJ

	\title{Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains}

@@

	\par The concept of heating the solar corona by nanoflares, first proposed by \citet{parker_nanoflares_1988}, has been developed extensively over the past two decades \citep[e.g.][]{cargill_implications_1994,cargill_nanoflare_2004,klimchuk_solving_2006}. The term \textit{nanoflare} has now become synonomous with impulsive heating in the energy range $10^{24}-10^{27}$ erg, with no specific assumption regarding the underlying physical mechanism (for example, small-scale magnetic reconnection or hydromagnetic wave dissipation).
	In active region (AR) cores such as those we discuss in this paper, one strategy for constraining potential heating models is the analysis of the emission measure distribution as a function of temperature, $\mathrm{EM}(T)=\int n^2\mathrm{d}h$. \citet{cargill_implications_1994,cargill_nanoflare_2004} predicted that $\mathrm{EM}(T)$ resulting from nanoflare heating should be wide, with a maximum value at $T=T_m\sim10^{6.5}$ K and have a faint, high-temperature (8-10 MK) component. Below $T_m$, there is a scaling $\mathrm{EM}(T)\sim T^a$ over a temperature range $10^6\lesssim T\lesssim T_m$, a result first discussed by \citet{jordan_structure_1975}. Observations from instruments onboard the Solar Dynamics Observatory \citep[SDO,][]{pesnell_solar_2012} and \textit{Hinode} spacecraft \citep{kosugi_hinode_2007} have shown that $2\lesssim a\lesssim5$, with $T_m\approx10^{6.5-6.6}$ \citep{warren_constraints_2011,warren_systematic_2012,winebarger_using_2011,tripathi_emission_2011,schmelz_cold_2012,del_zanna_evolution_2015}.

@@

	\par A scaling has been claimed for hot emission with $T>T_m$ such that $\mathrm{EM}\propto T^{-b}$, with $b>0$. This fit is usually done in the range $T_m\lesssim T\lesssim10^{7.2}$. However, measured values of these ``hotward" slopes are poorly constrained due to both the low magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}. \citet{warren_systematic_2012} find $7\lesssim b\lesssim10$ with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$. It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with different inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013}.

@@

	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release along a single magnetic strand, where the observed loop comprises many such strands. Nanoflare heating can be classified as being either a \textit{high-} or \textit{low-frequency}. In the case of high-frequency (HF) heating, $t_N$, the time between successive events, is such that $t_N\ll\tau_{cool}$, where $\tau_{cool}$ is a characteristic loop cooling time, and in the case of low-frequency (LF) heating $t_N\gg\tau_{cool}$ \citep{mulu-moore_can_2011,warren_constraints_2011,bradshaw_diagnosing_2012,reep_diagnosing_2013,cargill_modelling_2015}. Steady heating is just high-frequency heating in the limit $t_N\to0$. While a determination of $t_N$ is of great importance, its measurement is challenging. For example, while direct observations of possible reconnection-associated heating through short timescale changes in loop structure and emission is feasible, as demonsrated by the Hi-C rocket flight \citep{cirtain_energy_2013,cargill_solar_2013}, longer duration observations are required to constrain $t_N$. The previously-mentioned difficulties in reconstructing $\mathrm{EM}(T)$ must also be bourne in mind. Efforts to measure the heating frequency using narrow-band observations of intensity fluctuations in AR cores  have proved similarly difficult \citep{ugarte-urra_determining_2014}.

@@

	\par Single nanoflare are a good proxy for the LF heating scenario, but a study of nanoflare heating over a range of heating frequencies requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}. In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$. Preferential species heating, NEI, power-law nanoflare distributions, and the effects of a variable $t_N$ between events are considered and an emission measure ratio metric, similar to that discussed in \citet{brosius_pervasive_2014}, is used to characterize the various results. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure distributions and diagnostics for the entire parameter space. Finally, \autoref{sec:conclusions} discusses how our results may be interpreted in the broader context of nanoflare heating and provides some concluding comments on our findings.

@@

	\par In order to treat the evolution of the electron and ion populations separately, we use a modified version of the usual EBTEL equations. This amounts to computing spatial averages of the two-fluid hydrodynamic equations over both the transition region and corona. A full description and derivation of these equations can be found in the appendix of \citetalias{barnes_inference_2016-1}. The relevant two-fluid pressure and density equations are,

@@

	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency, and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional modifications detailed in Appendix 1 of \citetalias{barnes_inference_2016-1}. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$. In the cases where we treat the plasma as a single-fluid, we use the original EBTEL model as described in \citet{klimchuk_highly_2008,cargill_enthalpy-based_2012}.

@@

		\caption{Examples of four different heating functions: uniform heating amplitudes for $t_N=1000$ s (top), uniform heating amplitudes for $t_N=5000$ s (middle), and heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$ (bottom). In the bottom panel, the events shown in red have waiting times that depend on the previous event energy while the events shown in blue have uniform waiting times. The average waiting time in both cases is $t_N=2000$ s.}

@@

	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{m}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the time-averaged volumetric heating rate needed to keep a loop of half-length $L=40$ Mm at $\bar{T}\approx4$ MK as  $H_{eq}\sim3.6\times10^{-3}$. In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored. Thus, to maintain an emission measure peaked about $T_{m}$, for triangular pulses, the individual event heating rates are constrained by,

@@

		\include{parameter_space_graphic}
		\caption{Total Parameter space covered. ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $\varepsilon\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent. Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions per heated species.}

@@

@@

	\par As in \citetalias{barnes_inference_2016-1}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results. Given a temperature ($T(t)$) and density ($n(t)$) profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$, that would be inferred by assuming ionization equilibrium. Using $T_{eff}$, we are then able to compute a corresponding NEI emission measure distribution, $\mathrm{EM}(T_{eff})$.

@@

	\par We now show the results of our nanoflare train simulations for each point in our multidimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), waiting time ($t_N$), and waiting-time/event energy relationship ($\beta$). In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s. The average interval between subsequent events is $t_N$ (in the uniform and $\beta=0$ cases, $t_{N,i}=t_N$ exactly for all $i$). We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$. In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016-1}. The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$. All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}. All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.

@@

		\caption{Fits to a sample emission measure distribution constructed from a loop plasma in which only the electrons were heated by events chosen from a power-law distribution with $\alpha=-2.5$ and equally spaced by an interval of $t_N=5000$ s. \textbf{Left:} $\mathrm{EM}(T)$ slope as a function of upper bound on fit interval for both the hot (red) and cool (blue) side of $\mathrm{EM}(T)$. The shading denotes the uncertainty of the fit. The bottom axis corresponds to the varying upper limit on the fit to the cool side while the top axis corresponds to the varying upper limit on the fit to the hot side. \textbf{Right:} $\mathrm{EM}(T)$ with the overlaid hot (red) and cool (blue) fit lines whose slopes correspond to those shown on the left. The cool power-law fits describe $\mathrm{EM}(T)$ for $T<4$ MK quite well while a similar fit on the hot side fails to accurately describe the shape of the emission measure distribution for $T>4$ MK.}

@@

		\par\citet{brosius_pervasive_2014} proposed another possible diagnostic for the hot non-flaring corona. Using observations of an active region from the \textit{EUNIS-13} sounding rocket, they found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside. They argue that this provides possible evidence for impulsive heating. This arises from the fact that the $\mathrm{EM}(T)$ distribution resulting from low- and intermediate-frequency nanoflares is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}: for example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 10^{6.2}$ K and $10^{6.9}$ K. This suggests that the approach of \citet{brosius_pervasive_2014} could be used for any pair of appropriate emission lines and is likely to be of particular use where very limited spectral coverage is available either above or below $T_m$. Indeed for impulsive heating of any kind, the generic $\mathrm{EM}(T)$ curve remains similar (though not identical) as the magnitude of the heating changes. For flare-like energy release one would expect the hot emission to be much greater than the cold emission, with the opposite in the quiet Sun.

@@

	\par Considering first the left hand panels, in the single fluid model the ratio is largely insensitive to $\alpha$ and is peaked sharply at $\sim0.75-1.0$ although the distribution peaks at slightly higher values for the $\beta=1$ case ($\sim1.25$). Note that the uniform heating results (whose median is denoted by the vertical purple line near $\sim0.5$) show emission measure ratios significantly less than those in the power law cases, consistent with the reduced hot emission shown in \autoref{fig:single_em}. For electron heating the ratio is again insensitive to $\alpha$, but is narrower and falls off more quickly toward higher emission measure ratios. The $\beta=0$ cases (for all $\alpha$) peak near $0.5$, with the $\beta=1$ cases all peaking at slightly higher values, but all less than 1. For ion heating the $\beta=0$ distributions peak at lower values compared to those with $\beta=1$. Again the results are relatively insensitive to $\alpha$. However, compared to the electron heating case, all of the distributions are much wider and peak at higher values, $\sim1.5$ for $\beta=0$ and $>2$ for $\beta=1$. Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$.

	\par Turning to the right hand panels, in the single-fluid model for $t_N\le4000$ s, the results cluster just near 1.0, though the $t_N=3000$ s distribution is slightly bimodal, peaking strongly at $\sim0.75$ and more weakly at $\sim1.25$. Additionally, the $t_N=5000$ s case peaks slightly higher at $\sim1.5$ and does not ``pile up'' near 1.0 as the other values of $t_N$ do. For electron herating, the $t_N=3000$ s distribution has a very strong and narrow peak at $\approx0.5$ while all of the other distributions peak at $\sim1$. For $t_N\ge3000$ s, the location of the peak increases weakly with increasing $t_N$ though this is not the case for $t_N=1000,2000$ s. Finally, for ion heating the distributions for each value of $t_N$ are much wider than for a single fluid and electron heating and the peak values show a stronger dependence on $t_N$. The range of peak values is also much larger, with the $t_N=1000$ s case peaking near 0 and the $t_N=5000$ s case peaking at $\sim2$. As in \autoref{fig:em_ratio_hist_single}, we see that the $t_N=3000$ s distribution is bimodal. In general, the distributions grouped by $t_N$ for all three heating types have a positive skew and are peaked in the range $\sim0.5-1.5$ except for some extreme case in the ion heating scenario.

@@

	\par These results suggest that the emission measure ratio is generally in the range $\sim0.5-1.5$, with some higher values. Given the uncertainties in the atomic physics in particular, this seems to support the conclusion of the presence of nanoflare heating by \citet{brosius_pervasive_2014}. Thus the calculation of such ratios from limited data has the potential to be a powerful diagnostic of the existence of nanoflare heating. Whether one can say more about the precise form of nanoflare heating is less clear. In these results the ratios are largely independent of the power-law index $\alpha$ and only weakly-dependent on the waiting time, $t_N$. Furthermore, the distributions are also weakly dependent on the relationship between the waiting time and heating rate, $\beta$. The exception is the ion heating case where the distributions are much wider, peak at higher values, and show a stronger dependence on $\alpha$, $\beta$, and $t_N$. The problem with drawing conclusions from the details of these results lies in the numerous uncertainties in any data, especially concerning atomic physics.

@@

	\par Two possible ways to relate these results to present and future observations were discussed. First we showed that while below $T_m$ the well-known relation $\mathrm{EM}\sim T^a$ was quite robust, that was not the case above $T_m$. On the other hand the calculation of a ratio between the emission measure at a pair of temperatures above and below $T_m$ held more promise. For a wide range of parameters the ratio of the emission measure at two temperatures, $T_{hot}=10^{6.9}>T_m$ and $T_{cool}=10^{6.2}<T_m$, was of order unity, consistent with \citet{brosius_pervasive_2014} within various errors. Further observational evidence of such ratios would, in our view, provide a very strong case for the presence of nanoflare heating. On the other hand, given the uncertainties in atomic physics and emission emasure analysis, such a comparison seems unlikely to be able to shed more detailed light on the details (e.g. $t_N$, $\alpha$, $\beta$) of the actual heating process. 

@@

	\software{astroML \citep{vanderplas_introduction_2012}, IPython \citep{perez_ipython:_2007}, Jupyter notebook, matplotlib \citep{hunter_matplotlib:_2007}, NumPy, seaborn \citep{waskom_seaborn:_2016}, scipy \citep{van_der_walt_numpy_2011}}

@@

	%\bibliography{hot_non-flaring_plasma_2.bbl}

>>>>

	\title{Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores. II. Nanoflare Trains}

@@

	\par The concept of heating the solar corona by nanoflares, first proposed by \citet{parker_nanoflares_1988}, has been developed extensively over the past two decades \citep[e.g.][]{cargill_implications_1994,cargill_nanoflare_2004,klimchuk_solving_2006}. The term \textit{nanoflare} has now become synonomous with impulsive heating in the energy range $10^{24}-10^{27}$ erg, with no specific assumption regarding the underlying physical mechanism (for example, small-scale magnetic reconnection or hydromagnetic wave dissipation). In active region (AR) cores such as those we discuss in this paper, one strategy for constraining potential heating models is the analysis of the emission measure distribution as a function of temperature, $\mathrm{EM}(T)=\int n^2\mathrm{d}h$. \citet{cargill_implications_1994,cargill_nanoflare_2004} predicted that $\mathrm{EM}(T)$ resulting from nanoflare heating should be wide, with a maximum value at $T=T_m\sim10^{6.5}$ K and have a faint, high-temperature (8-10 MK) component. Below $T_m$, there is a scaling $\mathrm{EM}(T)\sim T^a$ over a temperature range $10^6\lesssim T\lesssim T_m$, a result first discussed by \citet{jordan_structure_1975}. Observations from instruments onboard the \textit{Solar Dynamics Observatory} \citep[\textit{SDO},][]{pesnell_solar_2012} and \textit{Hinode} spacecraft \citep{kosugi_hinode_2007} have shown that $2\lesssim a\lesssim5$, with $T_m\approx10^{6.5-6.6}$ \citep{tripathi_emission_2011,warren_constraints_2011,warren_systematic_2012,winebarger_using_2011,schmelz_cold_2012,del_zanna_evolution_2015}.

@@

	\par A scaling has been claimed for hot emission with $T>T_m$ such that $\mathrm{EM}\propto T^{-b}$, with $b>0$. This fit is usually done in the range $T_m\lesssim T\lesssim10^{7.2}$. However, measured values of these ``hotward" slopes are poorly constrained due to both the low magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}. \citet{warren_systematic_2012} find $7\lesssim b\lesssim10$ with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the \textit{Solar Maximum Mission}, claim larger values for $b$. It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with different inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013}.

@@

	\par An important parameter for any proposed coronal heating mechanism is the frequency of energy release along a single magnetic strand, where the observed loop comprises many such strands. Nanoflare heating can be classified as being either a \textit{high-} or \textit{low-frequency} (HF or LF, respectively). In the case of HF heating, $t_N$, the time between successive events, is such that $t_N\ll\tau_{cool}$, where $\tau_{cool}$ is a characteristic loop cooling time, and in the case of LF heating $t_N\gg\tau_{cool}$ \citep{mulu-moore_can_2011,warren_constraints_2011,bradshaw_diagnosing_2012,reep_diagnosing_2013,cargill_modelling_2015}. Steady heating is just HF heating in the limit $t_N\to0$. While a determination of $t_N$ is of great importance, its measurement is challenging. For example, while direct observations of possible reconnection-associated heating through short timescale changes in loop structure and emission is feasible, as demonsrated by the Hi-C rocket flight \citep{cirtain_energy_2013,cargill_solar_2013}, longer duration observations are required to constrain $t_N$. The previously-mentioned difficulties in reconstructing $\mathrm{EM}(T)$ must also be bourne in mind. Efforts to measure the heating frequency using narrow-band observations of intensity fluctuations in AR cores  have proved similarly difficult \citep{ugarte-urra_determining_2014}.

@@

	\par Single nanoflares are a good proxy for the LF heating scenario, but a study of nanoflare heating over a range of heating frequencies requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}. In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$. Preferential species heating, NEI, power-law nanoflare distributions, and the effects of a variable $t_N$ between events are considered and an emission measure ratio metric, similar to that discussed in \citet{brosius_pervasive_2014}, is used to characterize the various results. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure distributions and diagnostics for the entire parameter space. Finally, \autoref{sec:conclusions} discusses how our results may be interpreted in the broader context of nanoflare heating and provides some concluding comments on our findings.

@@

	\par In order to treat the evolution of the electron and ion populations separately, we use a modified version of the usual EBTEL equations. This amounts to computing spatial averages of the two-fluid hydrodynamic equations over both the transition region and corona. A full description and derivation of these equations can be found in Appendix B of \citetalias{barnes_inference_2016-1}. The relevant two-fluid pressure and density equations are,

@@

	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency, and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional modifications detailed in Appendix A of \citetalias{barnes_inference_2016-1}. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$. In the cases where we treat the plasma as a single-fluid, we use the original EBTEL model as described in \citet{klimchuk_highly_2008,cargill_enthalpy-based_2012}.

@@

		\caption{Examples of four different heating functions: uniform heating amplitudes for $t_N=1000$ s (top), uniform heating amplitudes for $t_N=5000$ s (middle), and heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$ (bottom). In the bottom panel, the events shown in red have waiting times that depend on the previous event energy ($\beta=1$) while the events shown in blue have uniform waiting times ($\beta=0$). The average waiting time in both cases is $t_N=2000$ s.}

@@

	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{m}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the time-averaged volumetric heating rate needed to keep a loop of half-length $L=40$ Mm at $\bar{T}\approx4$ MK as  $H_{eq}\sim3.6\times10^{-3}$ erg cm$^{-3}$ s$^{-1}$. In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored. Thus, to maintain an emission measure peaked about $T_{m}$, for triangular pulses, the individual event heating rates are constrained by,

@@

@@

		\input{../results/static/parameter_space_graphic}
		\caption{Total Parameter space covered. ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $\varepsilon\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent (i.e. $t_N$ is uniform). Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions per heated species.}

@@

	\par As in \citetalias{barnes_inference_2016-1}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results. Given a temperature and density profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$, that would be inferred by assuming ionization equilibrium. Using $T_{eff}$, we are then able to compute a corresponding NEI emission measure distribution, $\mathrm{EM}(T_{eff})$.

@@

	\par We now show the results of our nanoflare train simulations for each point in our multidimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), waiting time ($t_N$), and waiting-time/event energy relationship ($\beta$). In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s. The average interval between subsequent events is $t_N$ (in the uniform and $\beta=0$ cases, $t_{N,i}=t_N$ exactly for all $i$). We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$. In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016-1}. The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$. 

@@

		\caption{Fits to a sample emission measure distribution constructed from a loop plasma in which only the electrons were heated by events chosen from a power-law distribution with $\alpha=-2.5$ and equally spaced by an interval of $t_N=5000$ s. \textbf{Left:} Emission measure slope as a function of upper bound on the fit interval for both the hot (red) and cool (blue) side of $\mathrm{EM}(T)$. The shading denotes the uncertainty of the fit. The bottom axis corresponds to the varying upper limit on the fit to the cool side while the top axis corresponds to the varying upper limit on the fit to the hot side. \textbf{Right:} $\mathrm{EM}(T)$ with the overlaid hot (red) and cool (blue) fit lines whose slopes correspond to those shown on the left. The cool power-law fits describe $\mathrm{EM}(T)$ for $T<4$ MK quite well while a similar fit on the hot side fails to accurately describe the shape of $\mathrm{EM}(T)$ for $T>4$ MK.}

@@

		\par\citet{brosius_pervasive_2014} proposed another possible diagnostic for the hot non-flaring corona. Using observations of an active region from the \textit{EUNIS-13} sounding rocket, they found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside. They argue that this provides possible evidence for impulsive heating. This arises from the fact that the $\mathrm{EM}(T)$ distribution resulting from low- and intermediate-frequency nanoflares is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}. For example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 10^{6.2}$ K and $10^{6.9}$ K. This suggests that the approach of \citet{brosius_pervasive_2014} could be used for any pair of appropriate emission lines and is likely to be of particular use where very limited spectral coverage is available either above or below $T_m$. Indeed for impulsive heating of any kind, the generic $\mathrm{EM}(T)$ curve remains similar (though not identical) as the magnitude of the heating changes. For flare-like energy release one would expect the hot emission to be much greater than the cold emission, with the opposite in the quiet Sun.

@@

	\par Considering first the left hand panels, in the single fluid model (\autoref{fig:em_ratio_hist_single}) the ratio is largely insensitive to $\alpha$ and is peaked sharply at $\sim0.75-1.0$ although the distribution peaks at slightly higher values for the $\beta=1$ case ($\sim1.25$). Note that the uniform heating results (whose median is denoted by the vertical purple line near $\sim0.5$) show emission measure ratios significantly less than those in the power law cases, consistent with the reduced hot emission shown in \autoref{fig:single_em}. For electron heating (\autoref{fig:em_ratio_hist_el}) the ratio is again insensitive to $\alpha$, but is narrower and falls off more quickly toward higher emission measure ratios. The $\beta=0$ cases (for all $\alpha$) peak near $0.5$, with the $\beta=1$ cases all peaking at slightly higher values, but all less than 1. For ion heating (\autoref{fig:em_ratio_hist_ion}) the $\beta=0$ distributions peak at lower values compared to those with $\beta=1$. Again the results are relatively insensitive to $\alpha$. However, compared to the electron heating case, all of the distributions are much wider and peak at higher values, $\sim1.5$ for $\beta=0$ and $>2$ for $\beta=1$. Furthermore, in the $\beta=1$ case, the $\alpha=-2.5$ distribution peaks at lower values compared $\alpha=-1.5,-2.0$.

	\par Turning to the right hand panels, in the single-fluid model for $t_N\le4000$ s, the results cluster just near 1.0, though the $t_N=3000$ s distribution is slightly bimodal, peaking strongly at $\sim0.75$ and more weakly at $\sim1.25$. Additionally, the $t_N=5000$ s case peaks slightly higher at $\sim1.5$ and does not ``pile up'' near 1.0 as the other values of $t_N$ do. For electron heating, the $t_N=3000$ s distribution has a very strong and narrow peak at $\sim0.5$ while all of the other distributions peak at $\sim1$. For $t_N\ge3000$ s, the location of the peak increases weakly with increasing $t_N$ though this is not the case for $t_N=1000,2000$ s. Finally, for ion heating the distributions for each value of $t_N$ are much wider than for the single fluid and electron heating cases and the peak values show a stronger dependence on $t_N$. The range of peak values is also much larger, with the $t_N=1000$ s case peaking near 0 and the $t_N=5000$ s case peaking just above $2$. As in \autoref{fig:em_ratio_hist_single}, we see that the $t_N=3000$ s distribution is bimodal. In general, the distributions grouped by $t_N$ for all three heating types have a positive skew and are peaked in the range $\sim0.5-1.5$ except for some extreme cases in the ion heating scenario.

@@

	\par These results suggest that the emission measure ratio is generally in the range $\sim0.5-1.5$, with some higher values. Given the uncertainties in the atomic physics, This seems to support the conclusion of the presence of nanoflare heating by \citet{brosius_pervasive_2014}. Thus the calculation of such ratios from limited data has the potential to be a powerful diagnostic of the existence of nanoflare heating. Whether one can say more about the precise form of nanoflare heating is less clear. In these results the ratios are largely independent of the power-law index $\alpha$ and only weakly-dependent on the waiting time, $t_N$. Furthermore, the distributions are also weakly dependent on the relationship between the waiting time and heating rate, $\beta$. The exception is the ion heating case where the distributions are much wider, peak at higher values, and show a stronger dependence on $\alpha$, $\beta$, and $t_N$. The problem with drawing conclusions from the details of these results lies in the numerous uncertainties in any data, especially concerning atomic physics.

@@

	\par Two possible ways to relate these results to present and future observations were discussed. First we showed that while below $T_m$ the well-known relation $\mathrm{EM}\sim T^a$ was quite robust, that was not the case above $T_m$. On the other hand the calculation of a ratio between the emission measure at a pair of temperatures above and below $T_m$ held more promise. For a wide range of parameters the ratio of the emission measure at two temperatures, $T_{hot}=10^{6.95}>T_m$ and $T_{cool}=10^{6.2}<T_m$, was of order unity, consistent with \citet{brosius_pervasive_2014} within various errors. Further observational evidence of such ratios would, in our view, provide a very strong case for the presence of nanoflare heating. On the other hand, given the uncertainties in atomic physics and emission emasure analysis, such a comparison seems unlikely to be able to shed more detailed light on the details (e.g. $t_N$, $\alpha$, $\beta$) of the actual heating process. 

@@

	\software{astroML \citep{vanderplas_introduction_2012}, IPython/Jupyter \citep{perez_ipython:_2007}, matplotlib \citep{hunter_matplotlib:_2007}, NumPy, seaborn \citep{waskom_seaborn:_2016}, scipy \citep{van_der_walt_numpy_2011}}

@@
